Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-20 egpaper_supp.tex
suppl progress

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car32.png} &
  \includegraphics[width=0.40\linewidth]{supp/car26.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car10.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
  \includegraphics[width=0.40\linewidth]{supp/car8.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car31.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset, car
category. In each column, original image is on the left and detection result overlaid on
the right.}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset, bicycle
category. In each column, original image is on the left and detection result overlaid on
the right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
  \includegraphics[width=0.40\linewidth]{supp/car30.png} \\ 
  \includegraphics[width=0.40\linewidth]{supp/car18.png} &
  \includegraphics[width=0.40\linewidth]{supp/car25.png} \\
  \hline
  \end{tabular}
\caption{Failed detection or pose estimation results on 3D Object dataset, car
category. In each column, original image is on the left and detection result overlaid
on the right.}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
\hline 
  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle20.png} \\
\hline
\end{tabular}
\caption{Failed detection or pose estimation results on 3D Object dataset, bicycle
category. In each column, original image is on the left and detection result overlaid on
the right.}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_bad}
\end{figure*}

@@

  \caption{Detection and pose estimation on PASCAL3D+ dataset. On the left, we
  present average precision curve (red) average viewpoint precision curve
  (green). On the right, we present confusion matrix and mean precision in pose
  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
  $n-1$ is front-left for number of viewpoints $n$.}

>>>>

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car32.png} &
  \includegraphics[width=0.40\linewidth]{supp/car26.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car10.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
  \includegraphics[width=0.40\linewidth]{supp/car8.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car31.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object
  Classes~\cite{savarese07} cars. Original image (left) and overlaid
  detection result (right).}% with a bounding box and corresponding
                            % confidence score (right).}
  \label{fig:3dobject_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object
  Classes~\cite{savarese07} bicycles. Original image (left) and
  overlaid detection result (right).}
  \label{fig:3dobject_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
  \includegraphics[width=0.40\linewidth]{supp/car30.png} \\ 
  \includegraphics[width=0.40\linewidth]{supp/car18.png} &
  \includegraphics[width=0.40\linewidth]{supp/car25.png} \\
  \hline
  \end{tabular}
\caption{Failed detection or pose estimation on 3D Object
  Classes~\cite{savarese07} cars. Original image (left) and overlaid
  detection result (right).}
  \label{fig:3dobject_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
\hline 
  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle20.png} \\
\hline
\end{tabular}
\caption{Failed detection or pose estimation on 3D Object
  Classes~\cite{savarese07} bicycles. Original image (left) and overlaid
  detection result (right).}
  \label{fig:3dobject_bicycle_bad}
\end{figure*}

@@

  \caption{Detection and pose estimation on PASCAL3D+~\cite{Xiang14}
    cars and bicycles.
    Average Precision (red) and Average Viewpoint Precision (green)
    are given in the left plot and viewpoint confusion table and MPPE
    are given in the right plot. The viewpoint index 1 is front, 2 is
    front-right, \dots, $n-1$ is front-left for number of viewpoints $n$.}
 % On the left, we
 %  present average precision curve (red) average viewpoint precision curve
 %  (green). On the right, we present confusion matrix and mean precision in pose
 %  estimation. Viewpoint index 1 is front, index 2 is front-right \dots and
 %  $n-1$ is front-left for number of viewpoints $n$.}
